plyranges: a grammar for transforming genomics data

### 2018-04-09 paper.Rmd
more rearranging

>>>>

The most general Bioconductor data structure, GRanges, is capable of
representing all types of genomic data at a semantic level that
roughly matches the intuition of most users.  A GRanges is essentially
a table, with columns for the chromosome, stand and end coordinates,
and the strand, along with an arbitrary set of additional columns,
consisting of measurements or metadata specific to the data type or
experiment.  For example, a gene can be represented by its chromosomal
coordinates, along with its identifier and the identifiers of its
exons; or an RNA-seq experiment may be represented as sets of genes
with a matching count column.

GRanges follows the tidy data pattern: it is a rectangular table
corresponding to a single biological context. Each row contains a
single observation and each column is a variable about that
observation.
